Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-11-20 paper.tex
debug for adjust route

As far as we know, 
algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
with lower capacity. and in graph theory, algebraic connectivity value monotonically increased when we
increase the weight of link between vertices. So we extend the algebraic connectivity definition by following ways:

@@

If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
of this phase protect as much connectivity as possible. Following is our implementation:

>>>>

As far as we know, 
algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
with lower capacity. and in graph theory So we extend the algebraic connectivity definition by following ways:

@@

If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
of this phase protect as much connectivity as possible

Experiment shows that...
